IEEE: artikel

### 2015-04-10 Thesisfollowup/IEEE.tex
commit

 Not so long ago we discovered some high profile targeted attacks that infiltrated in a lot of systems without anyone noticing it. Belgacom [] has been the victim of a cyber security attack that has been uncovered for almost 2 years. The communication infrastructure of the Telecom company was infected with highly sophisticated malware making it possible to eavesdrop remotely. This means that even the most secure company can still be compromised without even noticing it. Such an attack can gain access to vulnerable data, credentials, cryptographic keys and many more. These kind of attacks that target organisations in a stealthy way and stay undetected for a long period are called APT (Advanced Persistent Threats).

\comment{uitleggen waarom we gametheorie gaan gebruiken om het spel te modelleren}
 The problem that we want to address in this article is how to react as a defender if our network system can be compromised by an attacker in a stealthy way. A research group at the RSA proposed a game to model the scenario where compromising the system is done stealthy and not immediately noticed by the system manager. In this FlipIt [1] game we have 2 players, the attacker and the defender, and a shared resource.
 Both players can gain at any time control of the shared resource, but this will always happen in a secretly manner. None of the players can observe who is in control of the resource. Every unit of time that a player is in control it gets utility. A player can 'flip' a resource which means that he is taking control over the resource. Each time the player flips the resource it has to pay a fixed cost.
 In this paper we want to model the problem of a corporate network that is under attack daily by viruses and worms. To do so we have to adapt the basic FlipIt game. Instead of one shared resource we have multiple resources that represent the nodes or devices in a corporate network. Each of these nodes are connected to other nodes by a graph.  \comment{email systeem }.

 The actions of the defender are. The actions of the attacker are. When system compromised

>>>>

 Not so long ago we discovered some high profile targeted attacks that infiltrated in a lot of systems without anyone noticing it. Belgacom \comment{[]} has been the victim of a cyber security attack that has been uncovered for almost 2 years. The communication infrastructure of the Telecom company was infected with highly sophisticated malware making it possible to eavesdrop remotely. This means that even the most secure company can still be compromised without even noticing it. Such an attack can gain access to vulnerable data, credentials, cryptographic keys and many more. These kind of attacks that target organisations in a stealthy way and stay undetected for a long period are called APT (Advanced Persistent Threats).

\comment{uitleggen waarom we gametheorie gaan gebruiken om het spel te modelleren}
 The problem that we want to address in this article is how to react as a defender if our network system can be compromised by an attacker in a stealthy way. A research group at the RSA proposed a game to model the scenario where compromising the system is done stealthy and not immediately noticed by the system manager. In this FlipIt \comment{[1]} game we have 2 players, the attacker and the defender, and a shared resource.
 Both players can gain at any time control of the shared resource, but this will always happen in a secretly manner. None of the players can observe who is in control of the resource. Every unit of time that a player is in control it gets utility. A player can 'flip' a resource which means that he is taking control over the resource. Each time the player flips the resource it has to pay a fixed cost.
 In this paper we want to model the problem of a corporate network that is under attack daily by viruses and worms. To do so we have to adapt the basic FlipIt game. Instead of one shared resource we have multiple resources that represent the nodes or devices in a corporate network. Each of these nodes are connected to other nodes by a graph. The connections represent the logical communication connections like a person in a contact list of an email application. The second adaptation is that when the attacker flips, it will drop a virus on that node. This virus will spread autonomously.
 In the following section we will describe the actions that the attacker and the defender can play.

 \subsection{actions of the defender}
 Dit is een generiek probleem. Het komt terug. 
 The actions of the defender are. The actions of the attacker are. When system compromised
